Delivering Reliable Software in the European Scientific Arena: Evolution of Methodologies and New Trend Analysis

### 2017-12-01 paper-ieee-trans.tex
added changes

\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
\title{Delivering reliable software in the European scientific arena: evolution of methodologies and new trend analysis}
%\title{15 years of European scientific software development: evolution and methodologies}

\author{E. Ronchieri,
        P. Orviz Fernandez,
        M. David,
		D.C. Duma,
        J. Gomes,
        D. Salomoni
\thanks{D. C. Duma, E. Ronchieri, and D. Salomoni are with INFN - CNAF, Bologna, Italy.}
\thanks{P. Orviz Fernandez, is with CSIC, Santander, Spain, (e-mail: orviz@ifca.unican.es)}
\thanks{M. David, and J. Gomes are with LIP, Lisbon, Portugal}%
}

% The paper headers
\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}

@@

\begin{IEEEbiography}{Michael Shell}
Biography text here.
\end{IEEEbiography}

% if you will not have a photo at all:
\begin{IEEEbiographynophoto}{John Doe}
Biography text here.
\end{IEEEbiographynophoto}

>>>>

%\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
\title{Delivering Reliable Software in the European Scientific Arena: Evolution of Methodologies and New Trend Analysis}
%\title{15 years of European scientific software development: evolution and methodologies}

\author{E. Ronchieri,
        P. Orviz Fernandez,
        M. David,
		D. C. Duma,
        J. Gomes,
        D. Salomoni
\thanks{D. C. Duma, E. Ronchieri, and D. Salomoni are with INFN - CNAF, Bologna, Italy.}
\thanks{P. Orviz Fernandez, is with CSIC, Santander, Spain, (e-mail: orviz@ifca.unican.es)}
\thanks{M. David, and J. Gomes are with LIP, Lisbon, Portugal}%
}

% The paper headers
%\markboth{IEEEtran for IEEE Journals}

@@

\begin{IEEEbiography} [{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/Ronchieri}}]{Elisabetta Ronchieri}
is a Computer Science Engineer at INFN (Istituto Nazionale di Fisica Nucleare - National Institute of Nuclear Physics) CNAF. Her main area of interest include software engineering issues such as software quality and software prediction model. She is also interested in (big and open) data analysis by using predictive techniques coming from various theories. such as Machine Learning.
\end{IEEEbiography}

P. Orviz Fernandez,
        M. David,
		D. C. Duma,
        J. Gomes,
        D. Salomoni

% if you will not have a photo at all:
\begin{IEEEbiography}{Pablo Orviz Fernandez}
Biography text here.
\end{IEEEbiography}

\begin{IEEEbiography}{Mario David}
Biography text here.
\end{IEEEbiography}

\begin{IEEEbiography}{D. Cristina Duma}
Biography text here.
\end{IEEEbiography}

\begin{IEEEbiography}{J. Gomes}
Biography text here.
\end{IEEEbiography}

\begin{IEEEbiography}{Davide Salomoni}
Biography text here.
\end{IEEEbiography}
